My title

### 2024-12-02 paper/paper.qmd
deleted unused files and finded abstract

---
title: "My title"
subtitle: "Impact Analysis of Japanese Occupation on Population Shifts Across Shanghai’s Districts During WWII"
author: 
  - Sandy Yu
thanks: "Code and data are available at: https://github.com/Jingying-yu/Shanghai_population_change"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

@@

We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...

@@

1940-06-22: France surrendered to Germany --> French Concession stopped taking refugees

@@

### Predictor variables
Time variable: year
Observations used in modelling and other analysis in this paper is ranged between 1936 to 1942. No observation is selected before 1936 as the growth pattern varies significantly from the event of our interest (Japanese occupation of Shanghai's different districts), and no value is elected beyond 1942 due to data constraints. No annual population records exists on a district bases beyond 1942. Foreign districts 解散 in 1949 as new political party came to power and the People's Republic of China was declared.

#### Binary Indicators
District indicators:
- Variable *district_is* abd *district_fc* are two binary variable used to indicate the district identity of an observation.
There are 3 possible district identity in Shanghai during 1930s-40s: Chinese-administrated District, International Settlement, and French Concession.

@@

Background details and diagnostics are included in Appendix \[@sec-model-details\].

@@

$$\alpha \sim \text{Normal}(0, 2.5)$$

$$\beta_k \sim \text{Normal}(0, 2.5) \quad \text{for } k = 1, ..., 11$$

@@

-   $y_i$: Observed population in district i at year t.
-   $\text{cd_occupied}$: Indicator for whether the Chinese-administered district was occupied by Japanese forces in year t (1 if $t \geq 1937$, 0 otherwise).
-   $\text{french_surrender}$: Indicator for the French Surrendering to Germany in 1940, leading to the French Concession rejecting refugees in Shanghai (1 if $t \geq 1940$, 0 otherwise).
-   $\text{is_occupied}$: Indicator for the Japanese occupation of the International Settlement in 1942 (1 if $t \geq 1942$, 0 otherwise).
-   $\text{district_type}$: Dummy variable for International Settlement districts (1 if $i$ is IS, 0 otherwise).
-   $\text{district_type}$: Dummy variable for French Concession districts (1 if $i$ is FC, 0 otherwise).

@@

-   $\text{cd_occupied} \cdot \text{district_type}$: Captures the effect of the 1937 occupation on the International Settlement in comparison to the Chinese-administered district (base district).
-   $\text{cd_occupied} \cdot \text{district_type}$: Captures the effect of the 1937 occupation on the French Concession in comparison to the base district.
-   $\text{french_surrender} \cdot \text{district_type}$: Effect of the 1940 refugee rejection on the International Settlement.
-   $\text{french_surrender} \cdot \text{district_type}$: Effect of the 1940 refugee rejection on the French Concession.
-   $\text{is_occupied} \cdot \text{district_type}$: Effect of the 1942 occupation on the International Settlement.
-   $\text{is_occupied} \cdot \text{district_type}$: Effect of the 1942 occupation on the French Concession.

@@

#### District Impact on Population
```{r}
#| echo: false
#| eval: true
#| label: tbl-district
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

@@

#### Historical Events
```{r}
#| echo: false
#| eval: true
#| label: tbl-events
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

@@

#### Historic Events' Impact on Each District
```{r}
#| echo: false
#| eval: true
#| label: tbl-events_district
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

@@

## Model Summary Table
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

>>>>

---
title: "My title"
subtitle: "Impact Analysis of Japanese Occupation on Population Shifts Across Shanghai’s Districts During WWII"
author: 
  - Sandy Yu
thanks: "Code and data are available at: https://github.com/Jingying-yu/Shanghai_population_change"
date: today
date-format: long
abstract: "This paper evaluates the impact of three historic events on the population dynamics of Shanghai during WWII: the Japanese occupation of the Chinese-administered area, France’s surrender in WWII, and the Japanese occupation of the International Settlement. Data from the Virtual Shanghai research platform and historic publications are analyzed using a difference-in-difference model to estimate the effects of these events. The results indicate that the Japanese occupation of the Chinese-administered area led to an overall increase in Shanghai’s population across all districts. In contrast, France’s surrender during WWII had a negative impact on population numbers in all districts except the French Concession. Similarly, the Japanese occupation of the International Settlement caused population declines in all districts except the International Settlement itself. These findings underscore the complex demographic shifts resulting from geopolitical events and reveal how wartime occupation reshaped urban populations in uneven ways, reflecting resilience and displacement patterns."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Analyses and findings in this paper are structured into several sections: @sec-data -- Data, @sec-model – Model, @sec-results -- Results, and @sec-discussion -- Discussion. The Data section examines all variables and attributes kept for analysis, followed by an explanation of their measurement and purpose. The Model section defines the generalized linear model used for further analysis, explain its components, and presents model justifications. The Result section focuses on visualizing and presenting the model results through data presented in Data section. The Discussion section further evaluate the interpretations behind the model results presented in the previous section, and touches on any expanded topics as well as weaknesses and next steps.

@@

Data is cleaned and analyzed using the open-source statistical programming language R [@citeR] and supporting packages including tidyverse [@tidyverse], arrow [@arrow], readr [@readr], knitr [@knitr], kableExtra [@kableExtra], modelsummary [@modelsummary], rstanarm [@rstanarm], dplyr [@dplyr], and broom.mixed [@broom.mixed]. These tools facilitate data manipulation, visualization, modeling, and reporting. Detailed descriptions of each dataset are provided in the subsections below.

@@

1940-06-22: France surrendered to Germany --\> French Concession stopped taking refugees

@@

### Predictor variables

Time variable: year Observations used in modelling and other analysis in this paper is ranged between 1936 to 1942. No observation is selected before 1936 as the growth pattern varies significantly from the event of our interest (Japanese occupation of Shanghai's different districts), and no value is elected beyond 1942 due to data constraints. No annual population records exists on a district bases beyond 1942. Foreign districts 解散 in 1949 as new political party came to power and the People's Republic of China was declared.

#### Binary Indicators

District indicators: - Variable *district_is* abd *district_fc* are two binary variable used to indicate the district identity of an observation. There are 3 possible district identity in Shanghai during 1930s-40s: Chinese-administrated District, International Settlement, and French Concession.

@@

Background details and diagnostics are included in Appendix [@sec-model-details].

@@

$$\mu_i = \alpha + \beta_k$$
$$\alpha \sim \text{Normal}(0, 2.5)$$

$$\beta_k \sim \text{Normal}(0, 2.5) \quad \text{for } k = 1, ..., 12$$

@@

-   $y_i$: Observed population in district i at year t.
-   $\alpha$: The intercept for when all variables take value of 0.
-   $\beta_1$: coefficient for temporal observation *year*. Controls for the effect of time (on an annual basis) on Shanghai's population.
-   $\beta_2$: coefficient for the dummy variable *district_is*. Take on value of 1 if the district of the observation is International Settlement districts (1 if *district type* is IS, 0 otherwise). The coefficient measures the effect of district identity on population of Shanghai within a given year.
-   $\beta_3$: *district_fc*: Dummy variable for French Concession districts (1 if $i$ is FC, 0 otherwise). The coefficient measures the effect of district identity on population of Shanghai within a given year.
-   $\beta_4$: the coefficient for *cd_occupied* indicator. This indicator takes a value of 1 after the Chinese-administered district was occupied by Japanese forces in year 1937 (1 if $t \geq 1937$, 0 otherwise). The coefficient measures the effect of this indicator on population of Shanghai within a given year.
-   $\beta_5$: coefficient for indicator *french_surrender* which takes on a value of *1* after the French Surrendering to Germany in 1940, leading to the French Concession rejecting refugees in Shanghai (1 if $t \geq 1940$, 0 otherwise). The coefficient measures the effect of this indicator on population of Shanghai within a given year.
-   $\beta_6$: the coefficient for the indicator *is_occupied*. This indicator marks the Japanese occupation of the International Settlement in 1942 (1 if $t \geq 1942$, 0 otherwise). The coefficient measures the effect of this indicator on population of Shanghai within a given year.
-   $\beta_i\ where\ i = 7, ..., 12$: coefficients for interaction terms below. Each term ajusts the impact of a historical events on a district-specific basis.

@@

-   *district_is × cd_occupied*: Captures the effect of the 1937 occupation on the International Settlement in comparison to the Chinese-administered district (base district).
-   *district_fc × cd_occupied*: Captures the effect of the 1937 occupation on the French Concession in comparison to the base district.
-   *district_is × french_surrender*: Effect of the 1940 refugee rejection on the International Settlement.
-   *district_fc × french_surrender*: Effect of the 1940 refugee rejection on the French Concession.
-   *district_is × is_occupied*: Effect of the 1942 occupation on the International Settlement.
-   *district_fc × is_occupied*: Effect of the 1942 occupation on the French Concession.

@@

#### District Impact on Population

```{r}
#| echo: false
#| eval: true
#| label: tbl-district
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

@@

#### Historical Events

```{r}
#| echo: false
#| eval: true
#| label: tbl-events
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

@@

#### Historic Events' Impact on Each District

```{r}
#| echo: false
#| eval: true
#| label: tbl-events_district
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

@@

## Model Summary Table

@@

# Appendix B: Idealized Survey Methodology

This appendix presents an idealized design for a population sampling survey, assuming that a data-recorder has unlimited time and authority to collect data within the historical timeframe of 1936–1942. The proposed methodology outlines a systematic approach to gathering detailed population data from Shanghai’s districts during pivotal wartime events, with considerations for the practical constraints and technology available during that period. While acknowledging the inherent challenges of conducting such a survey, this design aims to provide a comprehensive framework for understanding population dynamics within the Chinese-administered areas, International Settlement, and French Concession.

## Objective of the Survey

The purpose of this survey is to evaluate the relationship between key historical events and population shifts within Shanghai’s districts between 1936 and 1942. Specifically, the study aims to document the population changes in three major districts—Chinese-administered areas, International Settlement, and French Concession—during pivotal events such as the 1937 Japanese occupation of Chinese districts, the 1940 rejection of refugees in the French Concession, and the 1942 occupation of the International Settlement.

## Target Population

The survey targets residents and local representatives from the three major districts of Shanghai. These include long-term residents who were present before and during the historical events under study, as well as recent migrants and refugees arriving in these districts as a result of wartime displacement. The goal is to achieve representative coverage across the three districts to capture the diversity in population trends and movement patterns.

## Sampling Design

The sampling design employs stratified random sampling to ensure representation across the three major districts. Each district is treated as a separate stratum: Chinese-administered areas, International Settlement, and French Concession. A fixed number of households per district are selected based on district size, population density, and anticipated population shifts. Special attention is given to refugee populations within the International Settlement and French Concession to capture the impact of displacement. Enumerators use household lists and local community organizations, such as neighborhood associations and refugee aid committees, to randomly select respondents within strata.

## Recruitment Strategy

The recruitment strategy involves direct engagement with local leaders, community groups, and refugee aid organizations. Enumerators collaborate with influential figures in each district to gain trust and permission to conduct the survey. Recruitment booths are set up in public spaces such as markets and parks to engage with potential respondents. Additionally, refugee aid centers are utilized to access displaced populations. Recruitment materials are printed in both Chinese and English to accommodate the linguistic diversity of Shanghai’s residents.

## Survey Instrument

The survey instrument consists of a structured questionnaire covering demographic information, migration history, wartime impact, and population and housing details. The demographic section collects age, gender, occupation, family size, and household composition. Migration history includes the origin, year of migration to the current district, and reasons for relocation. Wartime impact focuses on displacement, property loss, and wartime experiences. Lastly, the population and housing section gathers data on the number of residents, housing type, and living conditions. Open-ended questions are also included to capture respondents’ personal narratives about wartime displacement and resettlement.

## Data Collection Procedures

Data collection occurs between 1936 and 1942, with enumerators visiting households, public spaces, and refugee shelters. Enumerators are trained to conduct interviews in Chinese, Shanghainese, or English based on respondent preferences. Responses are recorded on pre-printed forms, which are later transcribed and stored securely. To ensure accuracy, enumerators cross-check entries at the end of each survey day. Each enumerator is assigned a specific district to maintain consistency in data collection practices.

## Limitations and Challenges

Some areas, particularly those under military occupation, may not be accessible for data collection, leading to incomplete coverage. Additionally, respondents may underreport family size or migration history due to privacy concerns or fear of government reprisal. Refugee populations are often transient and may not remain in one location long enough for follow-up interviews. Despite these limitations, the survey employs robust sampling and recruitment strategies to mitigate potential biases.

## Ethical Considerations

Informed consent is obtained by informing respondents about the purpose of the survey and how their data will be used before they agree to participate. Personal identifying information is anonymized to ensure respondent privacy and security. Participation is entirely voluntary, and respondents can opt out at any time without consequences. The survey complies with ethical standards to respect the rights and dignity of all participants.
